Pythran: Bringing OpenMP to a Python Subset

### 2013-02-02 doc/papers/europar2013/paper.tex
Few cosmetic modifications

The core directive to handle data parallelism is the \texttt{for} directive that
distribute the iteration space of the associated loop among the existing
threads. To be compatible with OpenMP, the loop iteration space must be
described by a random access iterator with a total order, i.e.\ it is possible
to increase the iterator by any integer and to decide which iterator is the
greatest among two. The integer used as loop indices in Fortran and C satisfy
this conditions, so do C++ iterators with the \texttt{random\_access\_tag}
trait. But a Python iterator only advance by a step of one until it is
exhausted, in which case it raises an exception. They only have forward iterator
behavior.

@@

The \texttt{\_OPENMP} macro definition is always provided when OpenMP is
activated, and can be used for portability with system where OpenMP is not
available. Python does not have a preprocessor, but it is possible to catch the
import exception if the \texttt{omp} module is not found.

@@

We have used the Pythran tool described in the following section to turn each
Python test function into a C++ function with the same directives and runtime
calls. Apart from the \texttt{threadprivate} directive and the
\texttt{collapse(\emph{n})} clause, all tests were successful.
\texttt{threadprivate} directives were held by global variables not supported in
Pythran yet~; and the C++ code generated by Pythran does not preserve the perfect
loop nesting required by the \texttt{collapse} clause.

@@

All the source codes used for these benchmarks are availabe on the Pythran
reporsitory.~\footnote{\emph{cf}.\
\texttt{https://github.com/serge-sans-paille/pythran} on \texttt{europar2013}
branch.}

>>>>

The core directive to handle data parallelism is the \texttt{for} directive that
distribute the iteration space of the associated loop among the existing
threads. To be compatible with OpenMP, the loop iteration space must be
described by a random access iterator with a total order, that is possible
to increase the iterator by any integer and to decide which iterator is the
greatest among two. The integer used as loop indices in Fortran and C satisfy
this conditions, so do C++ iterators with the \texttt{random\_access\_tag}
trait. But a Python iterator only advance by a step of one until it is
exhausted, in which case it raises an exception. They only have forward iterator
behavior.

@@

The \texttt{\_OPENMP} macro definition is always provided when OpenMP is
activated, and can be used for portability with system where OpenMP is not
available. As Python does not have a preprocessor, it is possible to catch the
import exception if the \texttt{omp} module is not found.

@@

We have used the Pythran tool described in the following section to turn each
Python test function into a C++ function with the same directives and runtime
calls. Apart from the \texttt{threadprivate} directive and the
\texttt{collapse(\emph{n})} clause, all tests were successful.
\texttt{threadprivate} directives were held by global variables not supported in
Pythran~ yet; and the C++ code generated by Pythran does not preserve the perfect
loop nesting required by the \texttt{collapse} clause.

@@

Time mesure can be reproduce as procedure and test codes are available on 
developer repository~\footnote{\emph{cf}.\
\texttt{https://github.com/pbrunet/pythran} on \texttt{europar2013} branch}
